Pulmonary Exacerbations in CF

### 2024-01-02 Scott Sagel/PEx in CF/analysis_for_yaron.qmd
combined labels

```{r data cleaning}
# Import
df <- read.csv("./Scott Sagel/PEx in CF/Data_Raw/ExacerbationsInCF222_DATA_2024-01-02_0857.csv",
  na.strings = ""
)
# Get admit year (some missing in admit_year field)
df$year <- year(df$admit_date)
# Labels
labels <- list(
  "Aspergillus fumigatus" = "fungi___1",
  "Aspergillus (other species)" = "fungi___2",
  "Scedosporium apiospermum" = "fungi___3",
  "Candidia (any species)" = "fungi___4",
  "Other fungus" = "fungi___5",
  "NTM testing performed?" = "ntm_test",
  "M. abscessus species" = "ntm___1",
  "M. avium complex species" = "ntm___2",
  "Other NTM species" = "ntm___3",
  "A. xylosoxidans" = "bacteria_6months___1",
  "B. cepacia complex" = "bacteria_6months___2",
  "H. influenzae" = "bacteria_6months___3",
  "MRSA" = "bacteria_6months___4",
  "MSSA" = "bacteria_6months___5",
  "P. aeruginosa" = "bacteria_6months___6",
  "S. maltophilia" = "bacteria_6months___7",
  "Other bacteria" = "bacteria_6months___8"
)
labels <- setNames(names(labels), labels)
# Format
t <- df %>%
  select(
    sid, redcap_event_name, year, redcap_data_access_group,
    fungi___1:fungi___5,
    ntm_test, ntm___1:ntm___3,
    bacteria_6months___1:bacteria_6months___8
  ) %>%
  filter(!is.na(year))
```

```{r}
#| label: tbl-1
#| tbl-cap: Variable names
t %>%
  select(-sid, -redcap_event_name) %>%
  tbl_summary(by = year, missing_text = "Missing") %>%
  add_overall()
```

```{r}
#| label: tbl-2
#| tbl-cap: Labels
t %>%
  select(-sid, -redcap_event_name) %>%
  tbl_summary(
    by = year, missing_text = "Missing",
    label = labels
  ) %>%
  add_overall()
```

>>>>

```{r data cleaning}
# Import
df <- read.csv("./Scott Sagel/PEx in CF/Data_Raw/ExacerbationsInCF222_DATA_2024-01-02_0857.csv",
  na.strings = ""
)
# Get admit year (some missing in admit_year field)
df$year <- year(df$admit_date)
# Labels
labels <- list(
  "Aspergillus fumigatus" = "fungi___1",
  "Aspergillus (other species)" = "fungi___2",
  "Scedosporium apiospermum" = "fungi___3",
  "Candidia (any species)" = "fungi___4",
  "Other fungus" = "fungi___5",
  "NTM testing performed?" = "ntm_test",
  "M. abscessus species" = "ntm___1",
  "M. avium complex species" = "ntm___2",
  "Other NTM species" = "ntm___3",
  "A. xylosoxidans" = "bacteria_6months___1",
  "B. cepacia complex" = "bacteria_6months___2",
  "H. influenzae" = "bacteria_6months___3",
  "MRSA" = "bacteria_6months___4",
  "MSSA" = "bacteria_6months___5",
  "P. aeruginosa" = "bacteria_6months___6",
  "S. maltophilia" = "bacteria_6months___7",
  "Other bacteria" = "bacteria_6months___8"
)
labels <- setNames(paste0(names(labels)," (",labels,")"), labels)
# Format
t <- df %>%
  select(
    sid, redcap_event_name, year, redcap_data_access_group,
    fungal_test,fungi___1:fungi___5,
    ntm_test, ntm___1:ntm___3,
    bacteria_6months___1:bacteria_6months___8
  ) %>%
  filter(!is.na(year))
```

```{r}
#| label: tbl-1
#| tbl-cap: Variable names
t %>%
  select(-sid, -redcap_event_name) %>%
  tbl_summary(
    by = year, missing_text = "Missing",
    label = labels
  ) %>%
  add_overall()
```
